### 2021-06-25 JSS/using_drtmle_jss.Rmd

```{r, setup, include=FALSE}
options(prompt = 'R> ', continue = '+ ')
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
renv::activate(here::here())
library(nloptr)
```

>>>>

```{r, setup, include=FALSE}
options(prompt = 'R> ', continue = '+ ')
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
renv::activate(here::here())
library(nloptr); library(earth)
```
